### 2013-11-01 NeurounitFrontiers/Paper.tex
Updated acknowledgements

>>>>

\section{Acknowledgements}
We thank Sharon Crook, Jonathan Aldrich, Shreejoy Tripathy, and Padraig Gleeson for their support of this project.  
The work was supported in part by grant R01MH081905 from the National Institute of Mental Health. 
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
